---
title: "coan attempt (9/26)"
output: html_document
date: "2022-09-26"
---

all 96 samples unfiltered 

```{r}
library('vcfR')
library('poppr')
library('adegenet')
library('ggplot2')
library('dplyr')
library('tidyr')
library('stringr')
library('related')
library('tools')
```

```{r}
library(pegas)
```




```{r}
library(vcfR)
library(related)

vcf = read.vcfR('C:/Users/parsonsee/Desktop/subset_12samples.vcf')

geno = extract.gt(vcf)
G_relate = matrix(NA, nrow = ncol(geno), ncol = nrow(geno)*2)
abob = t(substr(geno, start = 1, stop = 1))
bbob = t(substr(geno, start = 3, stop = 3))
odd = seq(1, ncol(G_relate), by = 2)
G_relate[, odd] = abob
G_relate[, odd + 1] = bbob
rownames(G_relate) = rownames(abob)
colnames(G_relate) = rep(colnames(abob), each = 2)
class(G_relate) = "numeric"
G_relate = data.frame(Individual = rownames(G_relate), G_relate)
G_relate$Individual = as.character(G_relate$Individual)
G_relate[, 2:ncol(G_relate)] = G_relate[, 2:ncol(G_relate)] + 1 #to avoid 0s in data
```
```{r}
t(geno[1:5,1:5])
G_relate[1:5,1:10]
```




```{r}
relatedness <- coancestry(G_relate, wang=1)
```

```{r}
write.csv(dat, file = "C:/Users/parsonsee/Desktop/dat.csv")
```



```{r}
relatedness <- coancestry(dat, wang=1)
```




```{r}
vcf2 = read.vcfR('C:/Users/parsonsee/Desktop/subset_12samples.vcf')

geno = extract.gt(vcf2)
G_relate = matrix(NA, nrow = ncol(geno), ncol = nrow(geno)*2)
abob = t(substr(geno, start = 1, stop = 1))
bbob = t(substr(geno, start = 3, stop = 3))
odd = seq(1, ncol(G_relate), by = 2)
G_relate[, odd] = abob
G_relate[, odd + 1] = bbob
rownames(G_relate) = rownames(abob)
colnames(G_relate) = rep(colnames(abob), each = 2)
class(G_relate) = "numeric"
G_relate = data.frame(Individual = rownames(G_relate), G_relate)
G_relate$Individual = as.character(G_relate$Individual)
```
```{r}
t(geno[1:5,1:5])
G_relate[1:5,1:10]
```

```{r}
library('ggplot2')
library('dplyr')
library('tidyr')
```

```{r}
vcfdat<- vcfR2tidy(
  vcf2,
  info_only = FALSE,
  single_frame = TRUE,
  toss_INFO_column = TRUE
)

extract_info_tidy(vcf2, info_fields = NULL, info_types = TRUE, info_sep = ";")

extract_gt_tidy(
  vcf2,
  format_fields = NULL,
  format_types = TRUE,
  dot_is_NA = TRUE,
  alleles = TRUE,
  allele.sep = "/",
  gt_column_prepend = "gt_",
  verbose = TRUE
)

vcf_field_names(vcf2, tag = "INFO")
```
```{r}
gendat<- vcfdat$dat
```

```{r}
library(stringr)
```

```{r}
x <-gendat$gt_GT_alleles

gen <- str_split_fixed(x, "/", 2)
id <- gendat$Indiv
final <- cbind(id, gen)
final
```
```{r}
final <- head(final[c("id", "Allele1", "Allele2")])
```

```{r}
colnames(final) <- c('id','Allele1','Allele2')
```


```{r}
final <- as.data.frame(final)
head(final)
```

```{r}
write.csv(G_relate, file = "C:/Users/parsonsee/Desktop/G_relate.csv")
```

```{r}
final <- read.table("C:/Users/parsonsee/Desktop/grelate.txt", header=FALSE , sep="\t", stringsAsFactors =FALSE)
```

```{r}
final
```
```{r}
outfile <- coancestry (final, wang=1)
```





```{r}
#---Read data into R---#
input <- readgenotypedata(final)
```
```{r}
input
```


```{r}
library(related)
```


```{r}
#---Estimate relatedness---#
rel <- coancestry(input$gdata, lynchli=1, wang=1)
```


```{r}
		#---Create simulated individuals of known relatedness---#
sim <- familysim(input$freqs, 100)
```

```{r}
#---Compare relatedness estimators---#
compareestimators(input, 100)
```

```{r}
outfile <- coancestry("C:/Users/parsonsee/Desktop/grelate.txt", wang=1)
```


```{r}
#---Estimate relatedness---#
		rel <- coancestry(G_relate, lynchli=1, lynchrd=1, quellergt=1, wang=1)
```


```{r}
		#---Create simulated individuals of known relatedness---#
		sim <- familysim(G_relate, 100)
```

		#---Create simulated individuals of known relatedness---#
		sim <- familysim(input$freqs, 100)
```

```{r}
relat_fullDat = coancestry(G_relate, lynchli=1, lynchrd=1, quellergt=1, ritland=1, wang=1)
```

# write for delta7, delta8, relatedness, and inbreeding 

```{r}
write.csv(relat_fullDat$delta8, file = "C:/Users/parsonsee/Desktop/delta8.csv")
```



#all 96 samples hwe filtered 

```{r}
vcf = read.vcfR('C:/Users/parsonsee/Desktop/allhwe.vcf')

geno = extract.gt(vcf)
G_relate = matrix(NA, nrow = ncol(geno), ncol = nrow(geno)*2)
abob = t(substr(geno, start = 1, stop = 1))
bbob = t(substr(geno, start = 3, stop = 3))
odd = seq(1, ncol(G_relate), by = 2)
G_relate[, odd] = abob
G_relate[, odd + 1] = bbob
rownames(G_relate) = rownames(abob)
colnames(G_relate) = rep(colnames(abob), each = 2)
class(G_relate) = "numeric"
G_relate = data.frame(Individual = rownames(G_relate), G_relate)
G_relate$Individual = as.character(G_relate$Individual)
G_relate[, 2:ncol(G_relate)] = G_relate[, 2:ncol(G_relate)] + 1 #to avoid 0s in data
```

```{r}
relat_fullDat = coancestry(G_relate, lynchli=1, lynchrd=1, quellergt=1, ritland=1, wang=1)
```

# write for delta7, delta8, relatedness, and inbreeding 

```{r}
write.csv(relat_fullDat$delta8, file = "C:/Users/parsonsee/Desktop/delta8.csv")
write.csv(relat_fullDat$delta7, file = "C:/Users/parsonsee/Desktop/delta7.csv")
write.csv(relat_fullDat$inbreeding, file = "C:/Users/parsonsee/Desktop/inbreeding.csv")
```


```{r}
write.csv(relat_fullDat$relatedness, file = "C:/Users/parsonsee/Desktop/relatedness.csv")
```
