---
title: "IBS_Stats"
author: "Emily Parsons"
date: "2/9/2021"
output: html_document
---

Identity by state measurements vs. fertilization - all SNP variant data 

```{r}

install.packages("e1071")

```

```{r}
library(ggplot2)
library(car)
library(e1071)
```

```{r}
data1 <- read.csv("C:/Users/eepar/Desktop/2022all_time.csv")

data4 <- read.csv("C:/Users/eepar/Desktop/miles_2022.csv")
```


```{r}
#use spearman
shapiro.test(data1$fert) # => p = 0.1229
# Shapiro-Wilk normality test for wt
shapiro.test(data1$time) # => p = 0.09
```
```{r}
#use spearman
shapiro.test(data4$fert_sqrt) # => p = 0.1229
# Shapiro-Wilk normality test for wt
shapiro.test(data4$mi_sqrt) # => p = 0.09
```

```{r}
#USE spearman
shapiro.test(data2$fert) # => p = 0.1229
# Shapiro-Wilk normality test for wt
shapiro.test(data2$mi) # => p = 0.09
```
```{r}
#USE SPEARMAN
shapiro.test(data3$fert) # => p = 0.1229
# Shapiro-Wilk normality test for wt
shapiro.test(data3$mi) # => p = 0.09
```
```{r}
#USE PEARSON CORRELATION
shapiro.test(data4$fert_sqrt) # => p = 0.1229
# Shapiro-Wilk normality test for wt
shapiro.test(data4$mi_sqrt) # => p = 0.09
```

```{r}
  ggplot(data1, aes(x=direction, y=wang, fill=direction)) +
    geom_boxplot() + ggtitle("Directionality Boxplots: Night 2") +
  xlab("Direction") + ylab("Relatedness est") 
    
```


```{r}
library(e1071)
```

```{r}
displ1<-skewness(data$fert) 
displ1
```
```{r}
displ1_sqrt<-skewness(data$mi) 
displ1_sqrt
```
```{r}
displ2_log<-skewness(data$fert) 
displ2_log
```
```{r}
displ3_ln<-skewness(data3$mi) 
displ3_ln
```
```{r}
displ4_sq<-skewness(data4$mi) 
displ4_sq
```



If skewness value lies above +1 or below -1, data is highly skewed. If it lies between +0.5 to -0.5, it is moderately skewed. If the value is 0, then the data is symmetric
```{r}
displ2<-skewness(data1$mi) 
displ2
```
```{r}
displ2_sq <- skewness(data4$mi)
displ2_sq
```


If skewness value lies above +1 or below -1, data is highly skewed. If it lies between +0.5 to -0.5, it is moderately skewed. If the value is 0, then the data is symmetric

data are moderately to highly skewed towards the left 
```{r}
# Histogram overlaid with kernel density curve
ggplot(data, aes(x=mi_sqrt)) + ggtitle ("homog_king Genetic Distance Measures LN transformed: Histogram + Density Curve") +
  xlab("Genetic Distance") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666") 
# Overlay with transparent density plot
```

```{r}
# Histogram overlaid with kernel density curve
ggplot(data4, aes(x=mi)) + ggtitle("Night 1 Avergage Fert. Rates (Sq Transformed): Histogram + Density Curve") +
  xlab("Fertilization") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8, boundary = 9700,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666") 
# Overlay with transparent density plot
```


```{r}
summary(data$fert)
boxplot(data$fert, main ="Boxplot: King_homog genetic distance (LN transformed)", ylab="Genetic Relatedness", ylim=c(0,100))
qqnorm(data$fert, main ="Normal Q-Q Plot: King_homog genetic distance (LN transformed)")
qqline(data$fert)
```


```{r}
summary(data4$fert)
boxplot(data4$fert, main ="Boxplot: Night 1 Out-Crosses (Square Transformed)", ylab="Fertilization Rate", ylim=c(0,120))
qqnorm(data4$fert, main ="Normal Q-Q Plot: Night 1 Out-Crosses (Square Transformed)")
qqline(data4$fert)
```

```{r}
summary(data4$fert)
boxplot(data4$fert, main ="Boxplot: Night 1 Out-Crosses (Square Transformed)", ylab="Fertilization Rate", ylim=c(0,120))
qqnorm(data4$fert, main ="Normal Q-Q Plot: Night 1 Out-Crosses (Square Transformed)")
qqline(data4$fert)
```





```{r}
summary(data2$mi)
boxplot(data2$mi, main ="Boxplot: Night 1 Out-Crosses (Square Transformed)", ylab="Fertilization Rate", ylim=c(0,100))
qqnorm(data2$mi, main ="Normal Q-Q Plot: Night 1 Out-Crosses (Square Transformed)")
qqline(data2$mi)
```
```{r}
summary(data3$mi)
boxplot(data3$mi, main ="Boxplot: Night 1 Out-Crosses (Square Transformed)", ylab="Fertilization Rate", ylim=c(0,100))
qqnorm(data3$mi, main ="Normal Q-Q Plot: Night 1 Out-Crosses (Square Transformed)")
qqline(data3$mi)
```
```{r}
summary(data4$mi)
boxplot(data4$mi, main ="Boxplot: Night 1 Out-Crosses (Square Transformed)", ylab="Fertilization Rate", ylim=c(0,120))
qqnorm(data4$mi, main ="Normal Q-Q Plot: Night 1 Out-Crosses (Square Transformed)")
qqline(data4$mi)
```
```{r}
# Histogram overlaid with kernel density curve
ggplot(data2, aes(x=fert)) + ggtitle("Night 2 Avergae Fertilization Rates (Untransformed): Histogram + Density Curve") +
  xlab("Fertilization") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8, boundary = 100,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666")  # Overlay with transparent density plot

```

```{r}
# Histogram overlaid with kernel density curve
ggplot(gennorm, aes(x=lynchli_ln)) + ggtitle("Lynchli Method LN transformed: Histogram + Density Curve") +
  xlab("Genetic Relatedness") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8, boundary = 10000,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666")  # Overlay with transparent density plot

```

```{r}
summary(data2$fert)
boxplot(data2$fert, main ="Boxplot: Night 2 Out-Crosses (Untransformed)", ylab="Fertilization Rate", ylim=c(0,100))
qqnorm(data2$fert, main ="Normal Q-Q Plot: Night 2 Out-Crosses (Untransformed)")
qqline(data2$fert)
```


```{r}
summary(data2$fert_sq)
boxplot(data2$fert_sq, main ="Boxplot: Night 2 Out-Crosses (Square Transformed)", ylab="Fertilization Rate", ylim=c(0,10000))
qqnorm(data2$fert_sq, main ="Normal Q-Q Plot: Night 2 Out-Crosses (Square Transformed)")
qqline(data2$fert_sq)
```
GENETIC DATA

```{r}
gen1 <- skewness(data2$all_coan_wang)
gen2 <- skewness(data2$all_coan_lynchli)
gen3 <- skewness(data2$all_ibs_tassel_nohwe)
gen4 <- skewness(data2$related_all_nohwe)
gen5 <- skewness(data2$homog_all_nohwe)
gen6 <- skewness(data2$p_dist_all)
gen1
gen2
gen3
gen4
gen5
gen6
```

```{r}
gen1sq <- skewness(data2$all_coan_wang_sq)
gen2sq <- skewness(data2$all_coan_lynchli_sq)
gen3sq <- skewness(data2$all_ibs_tassel_nohwe_sq)
gen4sq <- skewness(data2$related_all_nohwe_sq)
gen5sq <- skewness(data2$homog_all_nohwe_sq)
gen6sq <- skewness(data2$p_dist_all_sq)
gen1sq
gen2sq
gen3sq
gen4sq
gen5sq
gen6sq
```

```{r}
gennorm <-  read.csv("C:/Users/parsonsee/Desktop/king_norm.csv")
```

```{r}
wang <- skewness(gennorm$wang)
wang_ln <- skewness(gennorm$wang_ln)
lynchli <- skewness(gennorm$lynchli)
lynchli_ln <- skewness(gennorm$lynchli_ln)
wang
wang_ln
lynchli
lynchli_ln
```


```{r}
summary(gennorm$homog)
boxplot(gennorm$homog, main ="Boxplot: Coancestry (Lynchli Method) LN transformed", ylab="Fertilization Rate", ylim=c(-1,1))
qqnorm(gennorm$homog, main ="Normal Q-Q Plot: Coancestry (Lynchli Method) LN transfored")
qqline(gennorm$homog)
```

```{r}
summary(gennorm$lynchli)
boxplot(gennorm$lynchli, main ="Boxplot: Coancestry (lynchli Method)", ylab="Genetic Relatedness", ylim=c(-0.105,0.05))
qqnorm(gennorm$lynchli, main ="Normal Q-Q Plot: Night 2 Coancestry (lynchli)")
qqline(gennorm$lynchli)
```

```{r}
gennorm1 <-  read.csv("C:/Users/parsonsee/Desktop/coan_norm1.csv")
```
```{r}
wang <- skewness(gennorm1$wang)
lynchli <- skewness(gennorm1$lynchli)
wang
lynchli
```

```{r}
summary(gennorm1$wang)
boxplot(gennorm1$wang, main ="Night 1 Boxplot: Coancestry (Wang Method)", ylab="Fertilization Rate", ylim=c(-0.08,-0.015))
qqnorm(gennorm1$wang, main ="Normal Q-Q Plot: Night 1 Coancestry (wang)")
qqline(gennorm1$wang)
```
```{r}
summary(gennorm1$lynchli)
boxplot(gennorm1$lynchli, main ="Boxplot: Coancestry (lynchli Method)", ylab="Genetic Relatedness", ylim=c(-0.08,-0.02))
qqnorm(gennorm1$lynchli, main ="Normal Q-Q Plot: Night 1 Coancestry (lynchli)")
qqline(gennorm1$lynchli)
```

OFAV Fert Data Night 1




```{r}
data <- read.csv("C:/Users/parsonsee/Desktop/ofavnight1.csv")
```

```{r}
s1 <- skewness(data$fert)
s1
s2 <- skewness(data$fert_sq)
s2
s3 <- skewness(data$fert_sqrt)
s3
s4 <- skewness(data$fert_ln)
s4
```
```{r}
summary(data$fert_sq)
boxplot(data$fert_sq, main ="Boxplot: OFAV Fert Results: Night 1 (SQ transformed)", ylab="Fertilization Rate", ylim=c(0,10000))
qqnorm(data$fert_sq, main ="Normal Q-Q Plot: OFAV Fert Results: Night 1 (SQ transformed)")
qqline(data$fert_sq)
```

If skewness value lies above +1 or below -1, data is highly skewed. If it lies between +0.5 to -0.5, it is moderately skewed. If the value is 0, then the data is symmetric

data are moderately to highly skewed towards the left 
```{r}
# Histogram overlaid with kernel density curve
ggplot(data, aes(x=fert)) + ggtitle ("OFAV Fert Results: Night 1 (Untransformed): Histogram + Density Curve") +
  xlab("Genetic Distance") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666") 
# Overlay with transparent density plot
```


```{r}
summary(data$fert_sq)
boxplot(data$fert_sq, main ="Boxplot: OFAV Fert Results: Night 1 (Untransformed)", ylab="Fertilization Rate", ylim=c(0,10000))
qqnorm(data$fert_sq, main ="Normal Q-Q Plot: OFAV Fert Results: Night 1 (Untransformed)")
qqline(data$fert_sq)
```
```{r}
# Histogram overlaid with kernel density curve
ggplot(data, aes(x=fert_sq)) + ggtitle ("OFAV Fert Results: Night 1 (Square transformed): Histogram + Density Curve") +
  xlab("Genetic Distance") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666") 
# Overlay with transparent density plot
```

```{r}
data <- read.csv("C:/Users/parsonsee/Desktop/ofavnight1.csv")
```

```{r}
displ <- skewness(data$fert_sq)
displ
```
```{r}
summary(data$fert)
boxplot(data$fert, main ="Boxplot: OFAV Fert Results: Night 1 (Untransformed)", ylab="Fertilization Rate", ylim=c(0,100))
qqnorm(data$fert, main ="Normal Q-Q Plot: OFAV Fert Results: Night 1 (Untransformed)")
qqline(data$fert)
```


OFAV 2022

```{r}
data <- read.csv("C:/Users/parsonsee/Desktop/ofav4time.csv")
```

```{r}
displ <- skewness(data$fert)
displ
displ2 <- skewness(data$fert_sq)
displ2
displ3 <- skewness(data$fert_sqrt)
displ3
displ4 <- skewness(data$fert_ln)
displ4
```

```{r}
summary(data$fert)
boxplot(data$fert, main ="Boxplot: 2022 OFAV Fert Results (Untransformed)", ylab="Fertilization Rate", ylim=c(0,100))
qqnorm(data$fert, main ="Normal Q-Q Plot: 2022 OFAV Fert Results (Untransformed)")
qqline(data$fert)
```

```{r}
summary(data$fert_sq)
boxplot(data$fert_sq, main ="Boxplot: 2022 OFAV Fert Results (Square transformed)", ylab="Fertilization Rate", ylim=c(0,10000))
qqnorm(data$fert_sq, main ="Normal Q-Q Plot: 2022 OFAV Fert Results (Square Untransformed)")
qqline(data$fert_sq)
```

```{r}
# Histogram overlaid with kernel density curve
ggplot(data, aes(x=fert)) + ggtitle ("2022 OFAV Fert Results (Untransformed): Histogram + Density Curve") +
  xlab("Genetic Distance") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666") 
# Overlay with transparent density plot
```

```{r}
# Histogram overlaid with kernel density curve
ggplot(data, aes(x=fert_sq)) + ggtitle ("2022 OFAV Fert Results (Square transformed): Histogram + Density Curve") +
  xlab("Genetic Distance") + ylab("Density") +
    geom_histogram(aes(y=..density..), bins = 8,
        colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666") 
# Overlay with transparent density plot
```