---
title: "Genetic distance X fertilization results"
author: "Erik Sotka"
date: "1/14/2021"
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

## Testing fertilization results of 12 crosses with identity by state values for each individual cross.  
### n=3 per cross

```{r}
library(lattice)
rm(list=ls())
dat <- read.csv("C:/Users/parsonsee/Desktop/night2.csv")
dat$parent1 <- unlist(lapply(strsplit(dat$cross,"-"),"[[",1))
dat$parent2 <- unlist(lapply(strsplit(dat$cross,"-"),"[[",2))

```

## Take the mean per cross and do analysis
### You lose the signal

```{r}
mean.fert <- tapply(dat$fert,dat$cross,mean)
mean.fert
```

## There was a parent 1 effect...

```{r}

m <- lm(fert_sq~parent1,data=dat)
anova(m)
```



```{r}
m <- lm(fert_sq~parent2,data=dat)
anova(m)
```

## Parent 2 effects that are significant have both positive and negative slopes

```{r}
plot(x=dat$wang_ln,y=dat$fert_sq,type="n")
unique2 <- unique(dat$parent2)
stats2 <- c()
for(i in 1:10)
{
  tmp <- dat[dat$parent2==unique1[i],]
  m <- lm(fert_sq~wang_ln,data=tmp)
  abline(m)
  stats2 <- rbind(stats2,data.frame(parent2=unique1[i],n=dim(tmp)[1],slope=summary(m)$coefficients[2],r2=round(summary(m)$r.squared,3),p=round(anova(m)$"Pr(>F)"[1],3)))
}
stats2$signif=ifelse(stats2$p<0.05,"*","")
print(stats2)
```

## When you ombine these parent1 or parent 2 effects, four of five significant slopes are positive.

```{r}
plot(x=dat$idbs,y=dat$fert,type="n")
unique1 <- unique(dat$parent1)
stats3 <- c()
for(i in 1:10)
{
  tmp <- dat[dat$parent1==unique1[i] | dat$parent2==unique1[i],]
  m <- lm(fert~idbs,data=tmp)
  abline(m)
  stats3 <- rbind(stats3,data.frame(parent=unique1[i],n=dim(tmp)[1],slope=summary(m)$coefficients[2],r2=round(summary(m)$r.squared,3),p=round(anova(m)$"Pr(>F)"[1],3)))
  
}
stats3$signif=ifelse(stats3$p<0.05,"*","")
print(stats3)
```



